---
title: "My Fancy Presentation for My Fancy Watermelon Sweetie Pie"
author: "Sukanya Basu"
date: "October 12, 2016"
output: ioslides_presentation
---



## My new slide
Some content

***
A slide without a title

## My title

### A top level subheading

#### A second level subheading


- Bullet 1
- Bullet 2

1. Item a
2. Item b

## My new slide

Plain text

*italicized text*

**Bold text**

` for (i %in% 1 : 10) `

## My new slide

```{r, comment = "", echo = TRUE}
head(mtcars)
```

```{r, comment = "", eval = FALSE}
head(mtcars)
```

## My new slide

```{r, echo = FALSE, fig.align='center', fig.cap='My AWESOME figure'}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

